---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Create map as a gift

The goal of mapartgift is to help create beautiful maps from OpenStreetMaps layers for your colleagues and family.

It is deeply inspired (almost forked) from https://taraskaduk.com/2019/12/20/print-maps/ and https://erdavis.com/2019/07/27/the-beautiful-hidden-logic-of-cities/ 

## Installation

You can install the package with 

``` r
devtools::install_github("tvroylandt/mapartgift")
```
## Package

The package contains two functions :

+ one to load the data ;
+ one to plot the map.

The fist step is to download the shapefiles into maps/shapefiles/region_name which can be done with the following chunk :

```{r download}
# url <- "http://download.geofabrik.de/europe/france/picardie-latest-free.shp.zip"
# curl::curl_download(url, destfile = "picardie.shp.zip")
# unzip("picardie.shp.zip", exdir = "inst/shapefiles/picardie")
```

After that you can make some maps. Just be careful with the CRS.

```{r packages}
library(mapartgift)
```

## Family

```{r family}


# Chantilly
# map_art_gift_load(
#   region = "picardie",
#   name_place = "Chantilly",
#   crs = 2154,
#   dist_shape = 3,
#   building = TRUE
# )
# map_art_gift_plot(
#   region = "picardie",
#   name_place = "Chantilly",
#   building = TRUE,
#   building_shp = building_cropped
# )

# Saint-Rimault
# map_art_gift_load(
#   region = "picardie",
#   name_place = "Saint-Rimault",
#   crs = 2154,
#   dist_shape = 2,
#   building = TRUE
# )
# map_art_gift_plot(
#   region = "picardie",
#   name_place = "Saint-Rimault",
#   building = TRUE,
#   building_shp = building_cropped
# )

# Lille
map_art_gift_load(
  region = "nord-pas-de-calais",
  name_place = "Lille",
  crs = 2154,
  dist_shape = 5,
  building = FALSE
)
map_art_gift_plot(region = "nord-pas-de-calais", name_place = "Lille")

# Paris
map_art_gift_load(
  region = "ile-de-france",
  name_place = "Paris",
  crs = 2154,
  dist_shape = 5
)
map_art_gift_plot(region = "ile-de-france", name_place = "Paris")

# Evanston
map_art_gift_load(
  region = "illinois",
  name_place = "Evanston",
  crs = 3528,
  dist_shape = 5
)
map_art_gift_plot(region = "illinois", name_place = "Evanston")

# Bruxelles
map_art_gift_load(
  region = "belgium",
  name_place = "Bruxelles - Brussel",
  crs = 3812,
  dist_shape = 5
)
map_art_gift_plot(region = "belgium", name_place = "Bruxelles - Brussel")
```


```{r assembly}
# library(magick)

```




















